Prepare Data

### 2021-04-13 src/data-processing/prep_data.Rmd
pap info

```{r "get data from Qualtrics"}
pret <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1)  %>%
  select(matches("PreT\\d"), id = ResponseId) %>%
  select(-matches("PreT[26]_NPS_GROUP")) %>%
  unite(order_PreT5, matches("PreT5_DO_\\d+"), sep="|") %>%
  unite(order_PreT7, matches("PreT7_DO_\\d+"), sep="|") %>%
  unite(order_PreT, matches("Pre-Treatment_DO_PreT\\d+"), sep="|") %>%
  select(id, PreT1:PreT5_4, PreT6:PreT7_5, 
         order_PreT5, order_PreT7, order_PreT) %>%
  mutate(across(matches("PreT5_\\d+"), 
            ~recode(., `15` = 5, `14` = 4, `13` = 3,
                    `12` = 2, `11` = 1)))

td <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(matches("FL_32"), id = ResponseId) %>%
  pivot_longer(cols = FL_32_DO_FL_104:FL_32_DO_FL_118,
               names_to = "Def") %>%
  drop_na(value) %>%
  mutate(Def = recode(Def,
                       `FL_32_DO_FL_104` = "Rachid Amezian + Compromis",
                       `FL_32_DO_FL_106` = "Rachid Amezian + Geen compromis",
                       `FL_32_DO_FL_108` = "Karel van der Kleijn + Compromis",
                       `FL_32_DO_FL_110` = "Karel van der Kleijn + Geen compromis",
                       `FL_32_DO_FL_112` = "Rachida Amezian + Compromis",
                       `FL_32_DO_FL_114` = "Rachida Amezian + Geen compromis",
                       `FL_32_DO_FL_116` = "Karin van der Kleijn + Compromis",
                       `FL_32_DO_FL_118` = "Karin van der Kleijn + Geen compromis")) %>%
  select(-value)

ti <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(matches("FL_78"), id = ResponseId) %>%
  pivot_longer(cols = FL_78_DO_FL_123:FL_78_DO_FL_142,
               names_to = "Imm") %>%
  drop_na(value) %>%
  mutate(Imm = recode(Imm,
                       `FL_78_DO_FL_123` = "Rachid Amezian + Compromis",
                       `FL_78_DO_FL_125` = "Rachid Amezian + Geen compromis",
                       `FL_78_DO_FL_129` = "Karel van der Kleijn + Compromis",
                       `FL_78_DO_FL_132` = "Karel van der Kleijn + Geen compromis",
                       `FL_78_DO_FL_134` = "Rachida Amezian + Compromis",
                       `FL_78_DO_FL_137` = "Rachida Amezian + Geen compromis",
                       `FL_32_DO_FL_139` = "Karin van der Kleijn + Compromis",
                       `FL_32_DO_FL_142` = "Karin van der Kleijn + Geen compromis"))  %>%
  select(-value)

te <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(matches("FL_84"), id = ResponseId) %>%
  pivot_longer(cols = FL_84_DO_FL_144:FL_84_DO_FL_161,
               names_to = "Edu") %>%
  drop_na(value) %>%
  mutate(Edu = recode(Edu,
                       `FL_84_DO_FL_144` = "Rachid Amezian + Compromis",
                       `FL_84_DO_FL_145` = "Rachid Amezian + Geen compromis",
                       `FL_84_DO_FL_148` = "Karel van der Kleijn + Compromis",
                       `FL_84_DO_FL_151` = "Karel van der Kleijn + Geen compromis",
                       `FL_84_DO_FL_153` = "Rachida Amezian + Compromis",
                       `FL_84_DO_FL_157` = "Rachida Amezian + Geen compromis",
                       `FL_84_DO_FL_159` = "Karin van der Kleijn + Compromis",
                       `FL_84_DO_FL_161` = "Karin van der Kleijn + Geen compromis")) %>%
  select(-value)

tc <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(matches("FL_101"), id = ResponseId) %>%
  pivot_longer(cols = FL_101_DO_FL_163:FL_101_DO_FL_177,
               names_to = "COVID") %>%
  drop_na(value) %>%
  mutate(COVID = recode(COVID,
                       `FL_101_DO_FL_163` = "Rachid Amezian + Compromis",
                       `FL_101_DO_FL_165` = "Rachid Amezian + Geen compromis",
                       `FL_101_DO_FL_167` = "Karel van der Kleijn + Compromis",
                       `FL_101_DO_FL_169` = "Karel van der Kleijn + Geen compromis",
                       `FL_101_DO_FL_171` = "Rachida Amezian + Compromis",
                       `FL_101_DO_FL_173` = "Rachida Amezian + Geen compromis",
                       `FL_101_DO_FL_175` = "Karin van der Kleijn + Compromis",
                       `FL_101_DO_FL_177` = "Karin van der Kleijn + Geen compromis")) %>%
  select(-value)

@@

bg <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(id = ResponseId, matches("F\\d"), etnicity) %>%
  unite(order_F6, matches("F6_DO_\\d+"), sep="|") %>%
  select(id, F1:F3, F4 = F4_1_TEXT, F5 = etnicity, F6, F7:F8, order_F6)

d <- left_join(bg, pret, by = "id")
d <- left_join(d, td, by = "id")
d <- left_join(d, ti, by = "id")
d <- left_join(d, te, by = "id")
d <- left_join(d, tc, by = "id")
d <- left_join(d, pt, by = "id")
rm(bg, pret, td, ti, te, tc, pt)
```

>>>>

```{r "get data from Qualtrics"}
pret <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1)  %>%
  select(matches("PreT\\d"), id = ResponseId) %>%
  select(-matches("PreT[26]_NPS_GROUP")) %>%
  unite(order_PreT5, matches("PreT5_DO_\\d+"), sep="|") %>%
  unite(order_PreT7, matches("PreT7_DO_\\d+"), sep="|") %>%
  unite(order_PreT, matches("Pre-Treatment_DO_PreT\\d+"), sep="|") %>%
  select(id, PreT1:PreT5_4, PreT6:PreT7_7, PreT8, 
         order_PreT5, order_PreT7, order_PreT) %>%
  mutate(across(matches("PreT5_\\d+"), 
            ~recode(., `15` = 5, `14` = 4, `13` = 3,
                    `12` = 2, `11` = 1)))

tr <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                  label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(matches("name-[A-Z]"), compromis, id = ResponseId)

@@

bg <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(id = ResponseId, matches("F\\d"), etnicity) %>%
  unite(order_F6, matches("F6_DO_\\d+"), sep="|") %>%
  mutate(F1 = recode(F1, `1` = 0, `2` = 1, `3` = 2, `4` = 999)) %>%
  select(id, F1:F3, F4 = F4_1_TEXT, F5 = etnicity, F6, F7:F8, order_F6)

d <- left_join(bg, pret, by = "id")
d <- left_join(d, tr, by = "id")
d <- left_join(d, pt, by = "id")
rm(bg, pret, tr, pt)
```
